---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
example_data <- read.csv("tests/testthat/test-data/data_1.csv")
```

# Cragg
An R package to implement the Cragg-Donald test for weak instruments.

## Overview
Cragg is an R package to implement the [Cragg-Donald](https://doi.org/10.1017/S0266466600007519) test for weak instruments, using critical values from [Stock and Yogo](https://ssrn.com/abstract=1734933).
These tests quantify the degree to which weak instruments can undermine regression estimates for models with multiple endogenous variables / treatments.

### Main Features

* Calculates Cragg-Donald statistics for weak instruments.

* Recommends critical values for the Cragg-Donald Statistic based on the largest allowable bias relative to regular OLS or maximum Wald test size distortion.

## Installation
```{r, eval = FALSE}
#install.packages("devtools")
devtools::install_github("beniaminogreen/cragg")
```

## Usage
```{r}
library(cragg)
#Cragg-Donald Test
cragg_donald(
	~X1+X2+X3,	#Controls
	~D,			#Treatments
	~Z1 + Z2,	#Instruments
	data =example_data
)

stock_yogo_test(
	~X1+X2+X3,	#Controls
	~D,			#Treatments
	~Z1 + Z2,	#Instruments
	B=.1,		#Maximum Allowable Size Distortion
	size_bias="size", #Calculate critical value for size distortions
	data =example_data
)
```

